\documentclass{aa}

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{xcolor}

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\simg}{\ensuremath{[\mathrm{Si}/\mathrm{Mg}]}}
\newcommand{\mgfe}{\ensuremath{[\mathrm{Mg}/\mathrm{Fe}]}}
\newcommand{\mh}{\ensuremath{[\mathrm{M}/\mathrm{H}]}}

\begin{document}

\title{A brief early Si-rich enrichment channel in compact relic galaxy formation}

\author{Tereza~TODO\inst{1}
\and Collaborators~TODO\inst{2}}

\institute{
TODO: Institute 1
\and
TODO: Institute 2
}

\abstract
{Compact relic galaxies provide stringent tests of early chemical enrichment because their stellar populations formed rapidly and experienced little subsequent dilution. NGC~1277 is especially interesting because Eftekhari-style near-infrared (NIR) analysis suggests high silicon relative to magnesium, while a successful clean relic model predicts much lower \simg.}
{We test whether a short early Si-rich enrichment episode can raise the model \simg\ while preserving the relic fit in stellar mass, metallicity, \mgfe, and mass-to-light ratio.}
{We summarize copied-code yield-channel tests built on an environment-dependent, time-variable galaxy-wide IMF model, using IGIMF/GalIMF as the computational machinery/tool. We compare clean, pre-enriched, mixed PopIII/PISN-like, and timed PopIII/PISN-like Si-rich enrichment experiments. We also test E-MILES NIR-local weighting as a first-order bridge to the observed NIR indices.}
{The clean NGC~1277-like baseline has code-light \simg=0.058, and E-MILES NIR-local weighting raises this only to \simg=0.075. The best accepted timed model, \texttt{timed\_s0\_d40\_m170\_f0p35\_e1p00}, reaches E-MILES NIR-local \simg=0.499 while remaining within the adopted relic-fit tolerance box: $\Delta\mh=+0.095$, $\Delta\mgfe=-0.070$, $\Delta\log M=+0.137$, and $\Delta\log M/L=+0.053$. Extending the same channel to 50 Myr reaches $\simg_{\rm NIR}\simeq0.523$ but is rejected because metallicity, \mgfe, and stellar mass degrade.}
{The current framework reaches the lower high-Si regime but not the nominal Eftekhari-like value near $\simg\simeq0.67$ without additional yield selectivity, localized enrichment, or NIR abundance-response systematics. The reported values are chemical-evolution abundance proxies, not full spectral-index abundance inferences.}

\keywords{galaxies: abundances -- galaxies: elliptical and lenticular, cD -- galaxies: evolution -- galaxies: stellar content -- stars: luminosity function, mass function}

\maketitle

\input{sections/01_introduction}
\input{sections/02_baseline_model}
\input{sections/03_methods}
\input{sections/04_model_tests}
\input{sections/05_results}
\input{sections/06_discussion}
\input{sections/07_conclusions}
\input{sections/acknowledgements}

\bibliographystyle{aa}
\bibliography{references}

\end{document}
