\section{Discussion}

\subsection{Physical interpretation}

A brief early Si-rich channel can explain the lower high-Si regime without immediately breaking the relic fit. The accepted model suggests enrichment confined to the first few tens of Myr, before the model accumulates too much total metal mass or suppresses \mgfe\ beyond the accepted limit.

\subsection{Si/Mg, Mg/Fe, and relicness}

Relicness should correlate robustly with \mgfe: old compact relics form rapidly and avoid late Fe-rich dilution. Si/Mg is a more conditional relicness tracer. It may correlate with relicness only if an early Si-rich channel operated and if later accreted or extended star formation did not dilute the signal.

\subsection{Why normal ETGs may dilute toward ordinary Si/Mg}

Normal early-type galaxies can build more extended stellar populations through longer star-formation histories, mergers, and accretion. Those later populations can dilute an early high-Si component in both mass and light, pushing integrated \simg\ toward more ordinary values even if the earliest compact core was Si-rich.

The weak/moderate ETG control sequence sharpens this picture. Normal massive ETGs can remain on the calibrated mass--metallicity and mass--\mgfe\ relations while accepting only weak or moderate preserved Si-rich enrichment. The conservative control channel is the 20 Myr, $f=0.10$ case. Stronger channels become boundary cases for normal ETGs and should not be used as normal-ETG calibration without additional two-component dilution or core-mass refits.

This supports differential preservation. Normal ETGs may not require the absence of early PopIII/PISN-like enrichment; instead, they require a lower preserved fraction of that signature. Their additional stellar mass can be old and alpha-enhanced, as expected for high-redshift assembly, while still carrying lower \simg. This naturally preserves high \mgfe\ but moves \simg\ toward the normal ETG locus.

\subsection{Mg/Fe and Si/Mg are not redundant}

\mgfe\ traces rapid formation generally. A compact core and an old high-redshift envelope can both be Mg-enhanced if both formed rapidly. In contrast, \simg\ is more selective: it traces whether the brief early Si-rich channel was strongly preserved. The fixed control sequence therefore motivates using \mgfe\ as the calibration and rapid-formation constraint, while using \simg\ as the preservation tracer that distinguishes normal massive ETGs from NGC~1277-like relics.

\subsection{Caveats about NIR abundance-response calibration}

The model values are chemical-evolution abundance proxies, not full spectral-index inferences. The E-MILES tests use baseFe SSP spectra for flux weighting and baseline index measurement, but not abundance-variable response functions. A publication-level comparison to Eftekhari-style $[\mathrm{Si}/\mathrm{Fe}]$, \mgfe, and \simg\ needs response-calibrated SiI and MgI NIR modeling at the appropriate velocity dispersion and aperture.
